Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-01 ms.tex
update caption of W1 SGC figure

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w1_large_scale.eps, width=7.0in}
  \caption{\label{fig:w1_large} A sub-section of the region shown in Figure
           \ref{fig:w2_large}. Top: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Bottom: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. Scattered moonlight has effectively
           been completely eliminated in W1.}
 \end{center}
\end{figure*}

>>>>

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w1_large_scale.eps, width=7.0in}
  \caption{\label{fig:w1_large} A subsection of the region displayed in Figure
           \ref{fig:w2_large}, now shown in W1. Left: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Right: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames. Scattered moonlight has effectively
           been completely eliminated in W1. The
           two dashed red boxes show locations where Jupiter passed through
           the WISE field of view. The imprints of such planet sightings have 
           now been removed}
 \end{center}
\end{figure*}
